Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Muck around with graphs

\begin{figure}[tb]
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{The cumulative number of instances solved over time, for the induced and non-induced
    problems, with different values of $k$. We also show the results of iteratively decreasing $k$
    until a solution is found, and in the induced case, the performance of a leading maximum common
    subgraph algorithm.}\label{figure:runtimes}
\end{figure}

\begin{figure}[tb]
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The larger instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-mcsruntimes.pdf}
    \caption{The cumulative number of maximum common induced subgraph instances solved over time,
    comparing our decreasing $k$ approach with two state of the art
    solvers.}\label{figure:mcsruntimes}
\end{figure}

What about if we use instances designed for the maximum common subgraph problem? In
\cref{figure:mcsruntimes} we again compare these approaches, but using the first ten instances from
each family of a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
number of vertices in the pattern and target graphs is the same, which is not ideal for our
algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
performance to the other two approaches (which are much more correlated), which suggests that there
is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
simultaneously or in parallel, stopping when the two bounds meet in the middle.

>>>>

\begin{figure*}[tb]
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{In the first two plots, the cumulative number of instances solved over time, for the
        induced and non-induced problems, with different values of $k$. We also show the results of
        iteratively decreasing $k$ until a solution is found, and in the induced case, the
        performance of two leading maximum common subgraph algorithms. In the third plot, results
        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
        common induced subgraph instances.}\label{figure:runtimes}
\end{figure*}

\begin{figure*}[tb]
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The larger instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure*}

@@

What about if we use instances designed for the maximum common subgraph problem? In the third plot
in \cref{figure:runtimes} we again compare these approaches, but using the first ten instances from
each family of a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
number of vertices in the pattern and target graphs is the same, which is not ideal for our
algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
performance to the other two approaches (which are much more correlated), which suggests that there
is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
simultaneously or in parallel, stopping when the two bounds meet in the middle.
